---
title: "Unit test practice"
author: "Jaslyn Miura"
format: html
---

## Unit testing with the `testthat` package

First, install necessary packages
```{r}
# install.packages("testthat")
# install.packages("devtools")
# install.packages("remotes")

library(testthat)
library(devtools)
library(remotes)
```
Write a function to practcie unit test.

This function is going to find the mean value of each column, and then return the lowest and highest mean value calculated (in that order).

We would expect:
- the output to be numeric
- output should be a vector of length 2
- first value should be smaller than the second value

```{r}
mean_range <- function (df) {
  # return the mean values of each column
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE)
  # finds minimum and maximum values
  col_mean_max <- max(col_means)
  col_mean_min <- min(col_means)
  
  # return min and max values (in that order)
  return(c(col_mean_min, col_mean_max))
}

mean_range(df = mtcars)

```

Write some unit tests!
```{r}
# this function `#| include: false` doesn't include this chunk in our knitted doc

# test that the output is of length 2
expect_length(mean_range(df = mtcars), 2)

# test that first value is less than second value
expect_true(mean_range(mtcars)[1] < mean_range(mtcars)[2])

```

